ZCB Pricing

### 2018-07-28 ZCB Pricing .Rmd
ff

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(n)
  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=mean
  result
}

@@

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha,beta,sigma,t,T,r0){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r0)
}

@@

CIR_MC= function(alpha,beta,sigma,T,r0,n,s){

@@

# Therefore the control variates estimate:

@@

r_vec=seq(-0.4,0.5,0.005)
CR=NULL
N=NULL
for (i in 1:length(r_vec)){
  CR[i]=Crude_Monte_Carlo(r0=r_vec[i])
  if(CR[i])
}

Var=var(CR)
Var
CR
Crude_Monte_Carlo(r0=-0.4)
```

>>>>

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(n)
  z_m= z-mean(z) # Moment matching transformation of RV to match finite moments

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] # Simulate rates using the transformed rv 
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=mean
  result
}

@@

# We have decided to make use of the CIR model as our control variate process.
# Below is the closed form solution under the CIR model
bond_price_CIR <- function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08){
  h <- sqrt(alpha^(2)+2*sigma^(2))
  A <-(2*h*exp((alpha+h)*(T-t)/2)/(2*h+(alpha+h)*(exp((T-t)*(h))-1)))^((2*alpha*beta)/sigma^(2))
  B <-2*(exp((T-t)*(h))-1)/(2*h+(alpha+h)*(exp((T-t)*(h))-1))
  A*exp(-B*r0)
}

@@

CIR_MC= function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){

@@

}
bond_price_CIR()
CIR_MC()
# Therefore the control variates estimate:

@@
